### 2022-11-15 dissertation/chapters/08-results.tex
🚧 (results): New CD plots and tables

			\textbf{air\_quality}         & \cellcolor[rgb]{ .427,  .757,  .482}3.6409 ($\pm$2.259)                   & \cellcolor[rgb]{ .804,  .863,  .506}5.4312 ($\pm$2.62)  & \cellcolor[rgb]{ .388,  .745,  .482}3.4452 ($\pm$2.57)  & \cellcolor[rgb]{ .729,  .843,  .502}5.0817 ($\pm$2.762) & \cellcolor[rgb]{ .467,  .765,  .486}3.8194 ($\pm$2.229) & \cellcolor[rgb]{ 1,  .894,  .514}6.686 ($\pm$3.061)     & \cellcolor[rgb]{ .765,  .851,  .502}5.2441 ($\pm$3.162) & \cellcolor[rgb]{ 1,  .922,  .518}6.357 ($\pm$2.303)     & \cellcolor[rgb]{ .996,  .784,  .494}7.8204 ($\pm$2.265)  & \cellcolor[rgb]{ .984,  .588,  .455}9.9151 ($\pm$2.288)  & \cellcolor[rgb]{ .98,  .518,  .443}10.6613 ($\pm$1.606)  & \cellcolor[rgb]{ .973,  .412,  .42}11.7559 ($\pm$1.473)  & \cellcolor[rgb]{ .976,  .471,  .431}11.1419 ($\pm$2.236) \\

@@

			\textbf{fish\_toxicity}       & \cellcolor[rgb]{ .533,  .784,  .49}4.2645 ($\pm$2.614)                    & \cellcolor[rgb]{ .388,  .745,  .482}3.6022 ($\pm$2.445) & \cellcolor[rgb]{ .388,  .745,  .482}3.5946 ($\pm$2.329) & \cellcolor[rgb]{ .784,  .859,  .502}5.4118 ($\pm$2.665) & \cellcolor[rgb]{ .89,  .89,  .51}5.8914 ($\pm$2.629)    & \cellcolor[rgb]{ .875,  .886,  .51}5.829 ($\pm$2.856)   & \cellcolor[rgb]{ .996,  .788,  .494}7.914 ($\pm$3.429)  & \cellcolor[rgb]{ 1,  .922,  .518}6.3849 ($\pm$2.944)    & \cellcolor[rgb]{ 1,  .894,  .514}6.7043 ($\pm$2.82)      & \cellcolor[rgb]{ .996,  .82,  .498}7.5731 ($\pm$2.982)   & \cellcolor[rgb]{ .976,  .471,  .431}11.5785 ($\pm$1.459) & \cellcolor[rgb]{ .973,  .412,  .42}12.2301 ($\pm$1.382)  & \cellcolor[rgb]{ .984,  .608,  .459}10.0215 ($\pm$2.358) \\
			\textbf{forest\_fires}        & \cellcolor[rgb]{ .769,  .855,  .502}5.1559 ($\pm$2.922)                   & \cellcolor[rgb]{ .388,  .745,  .482}4.2688 ($\pm$2.984) & \cellcolor[rgb]{ .718,  .839,  .498}5.0355 ($\pm$3.143) & \cellcolor[rgb]{ .569,  .796,  .49}4.6935 ($\pm$2.759)  & \cellcolor[rgb]{ 1,  .922,  .518}5.6882 ($\pm$2.215)    & \cellcolor[rgb]{ .91,  .894,  .51}5.4839 ($\pm$3.107)   & \cellcolor[rgb]{ 1,  .859,  .506}6.5161 ($\pm$3.082)    & \cellcolor[rgb]{ .898,  .89,  .51}5.4591 ($\pm$2.668)   & \cellcolor[rgb]{ .996,  .796,  .494}7.3667 ($\pm$2.37)   & \cellcolor[rgb]{ 1,  .863,  .51}6.4796 ($\pm$3.354)      & \cellcolor[rgb]{ .98,  .529,  .443}10.8129 ($\pm$1.207)  & \cellcolor[rgb]{ .976,  .463,  .431}11.7065 ($\pm$1.325) & \cellcolor[rgb]{ .973,  .412,  .42}12.3333 ($\pm$1.923)  \\

@@

			\textbf{student\_performance} & \cellcolor[rgb]{ .388,  .745,  .482}2.5634 ($\pm$1.912)                   & \cellcolor[rgb]{ .98,  .506,  .439}11.3978 ($\pm$2.178) & \cellcolor[rgb]{ .973,  .412,  .42}12.4312 ($\pm$1.34)  & \cellcolor[rgb]{ .843,  .875,  .506}5.6624 ($\pm$3.57)  & \cellcolor[rgb]{ .478,  .769,  .486}3.1935 ($\pm$2.12)  & \cellcolor[rgb]{ .875,  .882,  .51}5.8634 ($\pm$3.159)  & \cellcolor[rgb]{ .514,  .78,  .486}3.4194 ($\pm$2.006)  & \cellcolor[rgb]{ 1,  .902,  .514}6.9333 ($\pm$2.44)     & \cellcolor[rgb]{ 1,  .886,  .514}7.1032 ($\pm$1.989)     & \cellcolor[rgb]{ .98,  .537,  .443}11.0624 ($\pm$1.067)  & \cellcolor[rgb]{ .988,  .918,  .514}6.6366 ($\pm$2.023)  & \cellcolor[rgb]{ 1,  .922,  .518}6.7011 ($\pm$2.242)     & \cellcolor[rgb]{ .996,  .804,  .498}8.0323 ($\pm$1.935)  \\
			\textbf{wine\_quality}        & \cellcolor[rgb]{ .569,  .796,  .49}3.2806 ($\pm$1.931)                    & \cellcolor[rgb]{ .388,  .745,  .482}2.1118 ($\pm$1.666) & \cellcolor[rgb]{ .624,  .812,  .494}3.6301 ($\pm$1.731) & \cellcolor[rgb]{ .808,  .863,  .506}4.7882 ($\pm$2.105) & \cellcolor[rgb]{ .706,  .835,  .498}4.1505 ($\pm$1.916) & \cellcolor[rgb]{ .871,  .882,  .51}5.1925 ($\pm$1.951)  & \cellcolor[rgb]{ 1,  .922,  .518}6.0011 ($\pm$2.404)    & \cellcolor[rgb]{ .988,  .647,  .467}9.5935 ($\pm$1.494) & \cellcolor[rgb]{ .984,  .588,  .455}10.3387 ($\pm$1.62)  & \cellcolor[rgb]{ .98,  .525,  .443}11.1602 ($\pm$1.773)  & \cellcolor[rgb]{ .992,  .722,  .482}8.6344 ($\pm$1.18)   & \cellcolor[rgb]{ .988,  .651,  .467}9.5269 ($\pm$1.341)  & \cellcolor[rgb]{ .973,  .412,  .42}12.5903 ($\pm$1.352)  \\

@@

			\textbf{air\_quality}               & \cellcolor[rgb]{ .651,  .82,  .494}0.2569 ($\pm$0.007)                    & \cellcolor[rgb]{ .827,  .871,  .506}0.2606 ($\pm$0.009) & \cellcolor[rgb]{ .388,  .745,  .482}0.2513 ($\pm$0.008) & \cellcolor[rgb]{ 1,  .922,  .518}0.2642 ($\pm$0.011)    & \cellcolor[rgb]{ .647,  .82,  .494}0.2568 ($\pm$0.006)  & \cellcolor[rgb]{ .996,  .827,  .502}0.2729 ($\pm$0.016) & \cellcolor[rgb]{ .647,  .82,  .494}0.2568 ($\pm$0.006)  & \cellcolor[rgb]{ .976,  .914,  .514}0.2637 ($\pm$0.007) & \cellcolor[rgb]{ .996,  .792,  .494}0.2759 ($\pm$0.008) & \cellcolor[rgb]{ .984,  .608,  .459}0.2923 ($\pm$0.023) & \cellcolor[rgb]{ .988,  .69,  .475}0.2852 ($\pm$0.015)  & \cellcolor[rgb]{ .984,  .604,  .459}0.2929 ($\pm$0.016) & \cellcolor[rgb]{ .973,  .412,  .42}0.3097 ($\pm$0.017)  \\

@@

			\textbf{fish\_toxicity}             & \cellcolor[rgb]{ .588,  .8,  .49}0.0991 ($\pm$0.008)                      & \cellcolor[rgb]{ .451,  .761,  .482}0.0972 ($\pm$0.007) & \cellcolor[rgb]{ .388,  .745,  .482}0.0963 ($\pm$0.008) & \cellcolor[rgb]{ 1,  .91,  .518}0.1056 ($\pm$0.008)     & \cellcolor[rgb]{ .831,  .871,  .506}0.1023 ($\pm$0.008) & \cellcolor[rgb]{ 1,  .922,  .518}0.1046 ($\pm$0.008)    & \cellcolor[rgb]{ .773,  .855,  .502}0.1016 ($\pm$0.009) & \cellcolor[rgb]{ .976,  .914,  .514}0.1043 ($\pm$0.009) & \cellcolor[rgb]{ 1,  .863,  .506}0.1093 ($\pm$0.009)    & \cellcolor[rgb]{ 1,  .855,  .506}0.1099 ($\pm$0.012)    & \cellcolor[rgb]{ .976,  .475,  .435}0.1393 ($\pm$0.012) & \cellcolor[rgb]{ .973,  .412,  .42}0.1441 ($\pm$0.012)  & \cellcolor[rgb]{ .992,  .733,  .482}0.1193 ($\pm$0.013) \\
			\textbf{forest\_fires}              & \cellcolor[rgb]{ 1,  .922,  .518}0.0643 ($\pm$0.04)                       & \cellcolor[rgb]{ .557,  .792,  .49}0.0527 ($\pm$0.039)  & \cellcolor[rgb]{ 1,  .922,  .518}0.0626 ($\pm$0.039)    & \cellcolor[rgb]{ .824,  .871,  .506}0.0586 ($\pm$0.034) & \cellcolor[rgb]{ .851,  .878,  .506}0.0592 ($\pm$0.032) & \cellcolor[rgb]{ 1,  .89,  .514}0.081 ($\pm$0.069)      & \cellcolor[rgb]{ .388,  .745,  .482}0.0488 ($\pm$0.032) & \cellcolor[rgb]{ .976,  .914,  .514}0.0621 ($\pm$0.038) & \cellcolor[rgb]{ .553,  .792,  .49}0.0526 ($\pm$0.026)  & \cellcolor[rgb]{ 1,  .914,  .518}0.0692 ($\pm$0.047)    & \cellcolor[rgb]{ .992,  .722,  .482}0.1806 ($\pm$0.008) & \cellcolor[rgb]{ .992,  .706,  .478}0.1885 ($\pm$0.01)  & \cellcolor[rgb]{ .973,  .412,  .42}0.3598 ($\pm$0.09)   \\

@@

			\textbf{student\_performance}       & \cellcolor[rgb]{ .388,  .745,  .482}0.1656 ($\pm$0.011)                   & \cellcolor[rgb]{ .98,  .522,  .443}0.4929 ($\pm$0.105)  & \cellcolor[rgb]{ .973,  .412,  .42}0.5724 ($\pm$0.054)  & \cellcolor[rgb]{ 1,  .855,  .506}0.2454 ($\pm$0.134)    & \cellcolor[rgb]{ .471,  .769,  .486}0.1697 ($\pm$0.011) & \cellcolor[rgb]{ 1,  .871,  .51}0.2359 ($\pm$0.102)     & \cellcolor[rgb]{ .49,  .773,  .486}0.1708 ($\pm$0.01)   & \cellcolor[rgb]{ .969,  .91,  .514}0.1947 ($\pm$0.014)  & \cellcolor[rgb]{ 1,  .922,  .518}0.1962 ($\pm$0.01)     & \cellcolor[rgb]{ .984,  .573,  .451}0.4565 ($\pm$0.049) & \cellcolor[rgb]{ .933,  .902,  .514}0.193 ($\pm$0.011)  & \cellcolor[rgb]{ .925,  .898,  .51}0.1925 ($\pm$0.011)  & \cellcolor[rgb]{ 1,  .918,  .518}0.2014 ($\pm$0.012)    \\
			\textbf{wine\_quality}              & \cellcolor[rgb]{ .631,  .816,  .494}1.0651 ($\pm$0.024)                   & \cellcolor[rgb]{ .388,  .745,  .482}1.0395 ($\pm$0.018) & \cellcolor[rgb]{ .502,  .776,  .486}1.0514 ($\pm$0.021) & \cellcolor[rgb]{ 1,  .922,  .518}1.1028 ($\pm$0.039)    & \cellcolor[rgb]{ .698,  .831,  .498}1.0718 ($\pm$0.025) & \cellcolor[rgb]{ .804,  .863,  .506}1.0827 ($\pm$0.026) & \cellcolor[rgb]{ .788,  .859,  .502}1.0809 ($\pm$0.021) & \cellcolor[rgb]{ .996,  .839,  .502}1.1666 ($\pm$0.03)  & \cellcolor[rgb]{ .992,  .725,  .482}1.2516 ($\pm$0.046) & \cellcolor[rgb]{ .988,  .659,  .467}1.3046 ($\pm$0.114) & \cellcolor[rgb]{ .996,  .843,  .502}1.1648 ($\pm$0.023) & \cellcolor[rgb]{ .996,  .824,  .502}1.1774 ($\pm$0.019) & \cellcolor[rgb]{ .973,  .412,  .42}1.4896 ($\pm$0.093)  \\

@@

	\label{tab:results:heuristic_pool:metrics}%

@@

		\begin{tabular}{rccccccccc}
			\textbf{epoch}                      & \multicolumn{1}{l}{\textbf{(all)}}          &                                                                           &                 &                &                                                                                    &                 &                &                 &                 \\
			\cmidrule{1-2}                      &                                             &                                                                           &                 &                &                                                                                    &                 &                &                 &                 \\
			                                    & \multicolumn{1}{l}{\textbf{heuristic pool}} & \multicolumn{1}{l}{\textbf{metrics}}                                      &                 &                &                                                                                    &                 &                &                 &                 \\
			\cmidrule{2-3}                      & \textbf{all}                                &                                                                           &                 & \textbf{gd}    &                                                                                    &                 & \textbf{mh}    &                 &                 \\
			\cmidrule{2-10}    \textbf{dataset} & \textbf{count}                              & \textbf{avg}                                                              & \textbf{std}    & \textbf{count} & \textbf{avg}                                                                       & \textbf{std}    & \textbf{count} & \textbf{avg}    & \textbf{std}    \\

@@

			abalone                             & 930                                         & 1.7946                                                                    & 0.6411          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.3828}          & 0.5604          & 930            & 2.8226          & 0.4198          \\
			adult                               & 930                                         & 2.8484                                                                    & 0.5058          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.1559}          & 0.4077          & 930            & 1.8989          & 0.4104          \\
			air quality                         & 930                                         & 2.1871                                                                    & 0.8153          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.6828}          & 0.7506          & 930            & 2.1301          & 0.7883          \\
			bank                                & 930                                         & 1.7731                                                                    & 0.5617          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.3215}          & 0.4920          & 930            & 2.9054          & 0.3341          \\
			bike                                & 930                                         & 1.6247                                                                    & 0.5529          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4387}          & 0.5321          & 930            & 2.9366          & 0.2808          \\
			car                                 & 930                                         & 1.5903                                                                    & 0.5113          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4409}          & 0.5180          & 930            & 2.9688          & 0.2275          \\
			diabetic                            & 930                                         & 2.4516                                                                    & 0.7353          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.2806}          & 0.5756          & 930            & 2.2677          & 0.5798          \\
			fish toxicity                       & 930                                         & 1.9903                                                                    & 0.8485          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.8344}          & 0.7684          & 930            & 2.1753          & 0.7959          \\
			forest fires                        & 930                                         & 2.0667                                                                    & 0.8338          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.8269}          & 0.7813          & 930            & 2.1065          & 0.8066          \\
			housing                             & 930                                         & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.6043} & 0.6869          & 930            & 1.6602                                                                             & 0.6648          & 930            & 2.7355          & 0.5238          \\
			iris                                & 930                                         & 1.8581                                                                    & 0.8005          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.7806}          & 0.7272          & 930            & 2.3613          & 0.7960          \\
			mushroom                            & 930                                         & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.5204} & 0.5815          & 930            & 1.5484                                                                             & 0.5273          & 930            & 2.9312          & 0.2890          \\
			parkinsons                          & 930                                         & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.5570} & 0.6238          & 930            & 1.6011                                                                             & 0.5915          & 930            & 2.8419          & 0.4448          \\
			student performance                 & 930                                         & 1.9828                                                                    & 0.8220          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.7903}          & 0.8480          & 930            & 2.2269          & 0.7152          \\
			wine quality                        & 930                                         & 1.5785                                                                    & 0.5498          & 930            & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{1.4935}          & 0.5630          & 930            & 2.9280          & 0.2938          \\

@@

			\textbf{overall}                    & \textbf{13950}                              & \textbf{1.8952}                                                           & \textbf{0.7730} & \textbf{13950} & \cellcolor[rgb]{ .776,  .937,  .808}\textcolor[rgb]{ 0,  .38,  0}{\textbf{1.5492}} & \textbf{0.6651} & \textbf{13950} & \textbf{2.5491} & \textbf{0.6684} \\

>>>>

			\textbf{air quality}         & \cellcolor[rgb]{ .427,  .757,  .482}3.6409 ($\pm$2.259)                   & \cellcolor[rgb]{ .804,  .863,  .506}5.4312 ($\pm$2.62)  & \cellcolor[rgb]{ .388,  .745,  .482}3.4452 ($\pm$2.57)  & \cellcolor[rgb]{ .729,  .843,  .502}5.0817 ($\pm$2.762) & \cellcolor[rgb]{ .467,  .765,  .486}3.8194 ($\pm$2.229) & \cellcolor[rgb]{ 1,  .894,  .514}6.686 ($\pm$3.061)     & \cellcolor[rgb]{ .765,  .851,  .502}5.2441 ($\pm$3.162) & \cellcolor[rgb]{ 1,  .922,  .518}6.357 ($\pm$2.303)     & \cellcolor[rgb]{ .996,  .784,  .494}7.8204 ($\pm$2.265)  & \cellcolor[rgb]{ .984,  .588,  .455}9.9151 ($\pm$2.288)  & \cellcolor[rgb]{ .98,  .518,  .443}10.6613 ($\pm$1.606)  & \cellcolor[rgb]{ .973,  .412,  .42}11.7559 ($\pm$1.473)  & \cellcolor[rgb]{ .976,  .471,  .431}11.1419 ($\pm$2.236) \\

@@

			\textbf{fish toxicity}       & \cellcolor[rgb]{ .533,  .784,  .49}4.2645 ($\pm$2.614)                    & \cellcolor[rgb]{ .388,  .745,  .482}3.6022 ($\pm$2.445) & \cellcolor[rgb]{ .388,  .745,  .482}3.5946 ($\pm$2.329) & \cellcolor[rgb]{ .784,  .859,  .502}5.4118 ($\pm$2.665) & \cellcolor[rgb]{ .89,  .89,  .51}5.8914 ($\pm$2.629)    & \cellcolor[rgb]{ .875,  .886,  .51}5.829 ($\pm$2.856)   & \cellcolor[rgb]{ .996,  .788,  .494}7.914 ($\pm$3.429)  & \cellcolor[rgb]{ 1,  .922,  .518}6.3849 ($\pm$2.944)    & \cellcolor[rgb]{ 1,  .894,  .514}6.7043 ($\pm$2.82)      & \cellcolor[rgb]{ .996,  .82,  .498}7.5731 ($\pm$2.982)   & \cellcolor[rgb]{ .976,  .471,  .431}11.5785 ($\pm$1.459) & \cellcolor[rgb]{ .973,  .412,  .42}12.2301 ($\pm$1.382)  & \cellcolor[rgb]{ .984,  .608,  .459}10.0215 ($\pm$2.358) \\
			\textbf{forest fires}        & \cellcolor[rgb]{ .769,  .855,  .502}5.1559 ($\pm$2.922)                   & \cellcolor[rgb]{ .388,  .745,  .482}4.2688 ($\pm$2.984) & \cellcolor[rgb]{ .718,  .839,  .498}5.0355 ($\pm$3.143) & \cellcolor[rgb]{ .569,  .796,  .49}4.6935 ($\pm$2.759)  & \cellcolor[rgb]{ 1,  .922,  .518}5.6882 ($\pm$2.215)    & \cellcolor[rgb]{ .91,  .894,  .51}5.4839 ($\pm$3.107)   & \cellcolor[rgb]{ 1,  .859,  .506}6.5161 ($\pm$3.082)    & \cellcolor[rgb]{ .898,  .89,  .51}5.4591 ($\pm$2.668)   & \cellcolor[rgb]{ .996,  .796,  .494}7.3667 ($\pm$2.37)   & \cellcolor[rgb]{ 1,  .863,  .51}6.4796 ($\pm$3.354)      & \cellcolor[rgb]{ .98,  .529,  .443}10.8129 ($\pm$1.207)  & \cellcolor[rgb]{ .976,  .463,  .431}11.7065 ($\pm$1.325) & \cellcolor[rgb]{ .973,  .412,  .42}12.3333 ($\pm$1.923)  \\

@@

			\textbf{student performance} & \cellcolor[rgb]{ .388,  .745,  .482}2.5634 ($\pm$1.912)                   & \cellcolor[rgb]{ .98,  .506,  .439}11.3978 ($\pm$2.178) & \cellcolor[rgb]{ .973,  .412,  .42}12.4312 ($\pm$1.34)  & \cellcolor[rgb]{ .843,  .875,  .506}5.6624 ($\pm$3.57)  & \cellcolor[rgb]{ .478,  .769,  .486}3.1935 ($\pm$2.12)  & \cellcolor[rgb]{ .875,  .882,  .51}5.8634 ($\pm$3.159)  & \cellcolor[rgb]{ .514,  .78,  .486}3.4194 ($\pm$2.006)  & \cellcolor[rgb]{ 1,  .902,  .514}6.9333 ($\pm$2.44)     & \cellcolor[rgb]{ 1,  .886,  .514}7.1032 ($\pm$1.989)     & \cellcolor[rgb]{ .98,  .537,  .443}11.0624 ($\pm$1.067)  & \cellcolor[rgb]{ .988,  .918,  .514}6.6366 ($\pm$2.023)  & \cellcolor[rgb]{ 1,  .922,  .518}6.7011 ($\pm$2.242)     & \cellcolor[rgb]{ .996,  .804,  .498}8.0323 ($\pm$1.935)  \\
			\textbf{wine quality}        & \cellcolor[rgb]{ .569,  .796,  .49}3.2806 ($\pm$1.931)                    & \cellcolor[rgb]{ .388,  .745,  .482}2.1118 ($\pm$1.666) & \cellcolor[rgb]{ .624,  .812,  .494}3.6301 ($\pm$1.731) & \cellcolor[rgb]{ .808,  .863,  .506}4.7882 ($\pm$2.105) & \cellcolor[rgb]{ .706,  .835,  .498}4.1505 ($\pm$1.916) & \cellcolor[rgb]{ .871,  .882,  .51}5.1925 ($\pm$1.951)  & \cellcolor[rgb]{ 1,  .922,  .518}6.0011 ($\pm$2.404)    & \cellcolor[rgb]{ .988,  .647,  .467}9.5935 ($\pm$1.494) & \cellcolor[rgb]{ .984,  .588,  .455}10.3387 ($\pm$1.62)  & \cellcolor[rgb]{ .98,  .525,  .443}11.1602 ($\pm$1.773)  & \cellcolor[rgb]{ .992,  .722,  .482}8.6344 ($\pm$1.18)   & \cellcolor[rgb]{ .988,  .651,  .467}9.5269 ($\pm$1.341)  & \cellcolor[rgb]{ .973,  .412,  .42}12.5903 ($\pm$1.352)  \\

@@

			\textbf{air quality}                & \cellcolor[rgb]{ .651,  .82,  .494}0.2569 ($\pm$0.007)                    & \cellcolor[rgb]{ .827,  .871,  .506}0.2606 ($\pm$0.009) & \cellcolor[rgb]{ .388,  .745,  .482}0.2513 ($\pm$0.008) & \cellcolor[rgb]{ 1,  .922,  .518}0.2642 ($\pm$0.011)    & \cellcolor[rgb]{ .647,  .82,  .494}0.2568 ($\pm$0.006)  & \cellcolor[rgb]{ .996,  .827,  .502}0.2729 ($\pm$0.016) & \cellcolor[rgb]{ .647,  .82,  .494}0.2568 ($\pm$0.006)  & \cellcolor[rgb]{ .976,  .914,  .514}0.2637 ($\pm$0.007) & \cellcolor[rgb]{ .996,  .792,  .494}0.2759 ($\pm$0.008) & \cellcolor[rgb]{ .984,  .608,  .459}0.2923 ($\pm$0.023) & \cellcolor[rgb]{ .988,  .69,  .475}0.2852 ($\pm$0.015)  & \cellcolor[rgb]{ .984,  .604,  .459}0.2929 ($\pm$0.016) & \cellcolor[rgb]{ .973,  .412,  .42}0.3097 ($\pm$0.017)  \\

@@

			\textbf{fish toxicity}              & \cellcolor[rgb]{ .588,  .8,  .49}0.0991 ($\pm$0.008)                      & \cellcolor[rgb]{ .451,  .761,  .482}0.0972 ($\pm$0.007) & \cellcolor[rgb]{ .388,  .745,  .482}0.0963 ($\pm$0.008) & \cellcolor[rgb]{ 1,  .91,  .518}0.1056 ($\pm$0.008)     & \cellcolor[rgb]{ .831,  .871,  .506}0.1023 ($\pm$0.008) & \cellcolor[rgb]{ 1,  .922,  .518}0.1046 ($\pm$0.008)    & \cellcolor[rgb]{ .773,  .855,  .502}0.1016 ($\pm$0.009) & \cellcolor[rgb]{ .976,  .914,  .514}0.1043 ($\pm$0.009) & \cellcolor[rgb]{ 1,  .863,  .506}0.1093 ($\pm$0.009)    & \cellcolor[rgb]{ 1,  .855,  .506}0.1099 ($\pm$0.012)    & \cellcolor[rgb]{ .976,  .475,  .435}0.1393 ($\pm$0.012) & \cellcolor[rgb]{ .973,  .412,  .42}0.1441 ($\pm$0.012)  & \cellcolor[rgb]{ .992,  .733,  .482}0.1193 ($\pm$0.013) \\
			\textbf{forest fires}               & \cellcolor[rgb]{ 1,  .922,  .518}0.0643 ($\pm$0.04)                       & \cellcolor[rgb]{ .557,  .792,  .49}0.0527 ($\pm$0.039)  & \cellcolor[rgb]{ 1,  .922,  .518}0.0626 ($\pm$0.039)    & \cellcolor[rgb]{ .824,  .871,  .506}0.0586 ($\pm$0.034) & \cellcolor[rgb]{ .851,  .878,  .506}0.0592 ($\pm$0.032) & \cellcolor[rgb]{ 1,  .89,  .514}0.081 ($\pm$0.069)      & \cellcolor[rgb]{ .388,  .745,  .482}0.0488 ($\pm$0.032) & \cellcolor[rgb]{ .976,  .914,  .514}0.0621 ($\pm$0.038) & \cellcolor[rgb]{ .553,  .792,  .49}0.0526 ($\pm$0.026)  & \cellcolor[rgb]{ 1,  .914,  .518}0.0692 ($\pm$0.047)    & \cellcolor[rgb]{ .992,  .722,  .482}0.1806 ($\pm$0.008) & \cellcolor[rgb]{ .992,  .706,  .478}0.1885 ($\pm$0.01)  & \cellcolor[rgb]{ .973,  .412,  .42}0.3598 ($\pm$0.09)   \\

@@

			\textbf{student performance}        & \cellcolor[rgb]{ .388,  .745,  .482}0.1656 ($\pm$0.011)                   & \cellcolor[rgb]{ .98,  .522,  .443}0.4929 ($\pm$0.105)  & \cellcolor[rgb]{ .973,  .412,  .42}0.5724 ($\pm$0.054)  & \cellcolor[rgb]{ 1,  .855,  .506}0.2454 ($\pm$0.134)    & \cellcolor[rgb]{ .471,  .769,  .486}0.1697 ($\pm$0.011) & \cellcolor[rgb]{ 1,  .871,  .51}0.2359 ($\pm$0.102)     & \cellcolor[rgb]{ .49,  .773,  .486}0.1708 ($\pm$0.01)   & \cellcolor[rgb]{ .969,  .91,  .514}0.1947 ($\pm$0.014)  & \cellcolor[rgb]{ 1,  .922,  .518}0.1962 ($\pm$0.01)     & \cellcolor[rgb]{ .984,  .573,  .451}0.4565 ($\pm$0.049) & \cellcolor[rgb]{ .933,  .902,  .514}0.193 ($\pm$0.011)  & \cellcolor[rgb]{ .925,  .898,  .51}0.1925 ($\pm$0.011)  & \cellcolor[rgb]{ 1,  .918,  .518}0.2014 ($\pm$0.012)    \\
			\textbf{wine quality}               & \cellcolor[rgb]{ .631,  .816,  .494}1.0651 ($\pm$0.024)                   & \cellcolor[rgb]{ .388,  .745,  .482}1.0395 ($\pm$0.018) & \cellcolor[rgb]{ .502,  .776,  .486}1.0514 ($\pm$0.021) & \cellcolor[rgb]{ 1,  .922,  .518}1.1028 ($\pm$0.039)    & \cellcolor[rgb]{ .698,  .831,  .498}1.0718 ($\pm$0.025) & \cellcolor[rgb]{ .804,  .863,  .506}1.0827 ($\pm$0.026) & \cellcolor[rgb]{ .788,  .859,  .502}1.0809 ($\pm$0.021) & \cellcolor[rgb]{ .996,  .839,  .502}1.1666 ($\pm$0.03)  & \cellcolor[rgb]{ .992,  .725,  .482}1.2516 ($\pm$0.046) & \cellcolor[rgb]{ .988,  .659,  .467}1.3046 ($\pm$0.114) & \cellcolor[rgb]{ .996,  .843,  .502}1.1648 ($\pm$0.023) & \cellcolor[rgb]{ .996,  .824,  .502}1.1774 ($\pm$0.019) & \cellcolor[rgb]{ .973,  .412,  .42}1.4896 ($\pm$0.093)  \\

@@

	\label{tab:results:heuristic_pool:metrics:rank}%

@@

		\begin{tabular}{r|ccc}
			                             & \multicolumn{3}{c}{\textbf{Heuristic Pool - Average Rank}}                                                                                                                    \\

@@

			\textbf{dataset}             & \textbf{all}                                               & \textbf{gd}                                             & \textbf{mh}                                            \\

@@

			\textbf{abalone}             & \cellcolor[rgb]{ 1,  .922,  .518}1.7946 ($\pm$0.641)       & \cellcolor[rgb]{ .388,  .745,  .482}1.3828 ($\pm$0.56)  & \cellcolor[rgb]{ .973,  .412,  .42}2.8226 ($\pm$0.42)  \\
			\textbf{air quality}         & \cellcolor[rgb]{ .973,  .412,  .42}2.1871 ($\pm$0.815)     & \cellcolor[rgb]{ .388,  .745,  .482}1.6828 ($\pm$0.751) & \cellcolor[rgb]{ 1,  .922,  .518}2.1301 ($\pm$0.788)   \\
			\textbf{bank}                & \cellcolor[rgb]{ 1,  .922,  .518}1.7731 ($\pm$0.562)       & \cellcolor[rgb]{ .388,  .745,  .482}1.3215 ($\pm$0.492) & \cellcolor[rgb]{ .973,  .412,  .42}2.9054 ($\pm$0.334) \\
			\textbf{bike}                & \cellcolor[rgb]{ 1,  .922,  .518}1.6247 ($\pm$0.553)       & \cellcolor[rgb]{ .388,  .745,  .482}1.4387 ($\pm$0.532) & \cellcolor[rgb]{ .973,  .412,  .42}2.9366 ($\pm$0.281) \\
			\textbf{car}                 & \cellcolor[rgb]{ 1,  .922,  .518}1.5903 ($\pm$0.511)       & \cellcolor[rgb]{ .388,  .745,  .482}1.4409 ($\pm$0.518) & \cellcolor[rgb]{ .973,  .412,  .42}2.9688 ($\pm$0.228) \\
			\textbf{diabetic}            & \cellcolor[rgb]{ .973,  .412,  .42}2.4516 ($\pm$0.735)     & \cellcolor[rgb]{ .388,  .745,  .482}1.2806 ($\pm$0.576) & \cellcolor[rgb]{ 1,  .922,  .518}2.2677 ($\pm$0.58)    \\
			\textbf{fish toxicity}       & \cellcolor[rgb]{ 1,  .922,  .518}1.9903 ($\pm$0.849)       & \cellcolor[rgb]{ .388,  .745,  .482}1.8344 ($\pm$0.768) & \cellcolor[rgb]{ .973,  .412,  .42}2.1753 ($\pm$0.796) \\
			\textbf{forest fires}        & \cellcolor[rgb]{ 1,  .922,  .518}2.0667 ($\pm$0.834)       & \cellcolor[rgb]{ .388,  .745,  .482}1.8269 ($\pm$0.781) & \cellcolor[rgb]{ .973,  .412,  .42}2.1065 ($\pm$0.807) \\
			\textbf{housing}             & \cellcolor[rgb]{ .388,  .745,  .482}1.6043 ($\pm$0.687)    & \cellcolor[rgb]{ 1,  .922,  .518}1.6602 ($\pm$0.665)    & \cellcolor[rgb]{ .973,  .412,  .42}2.7355 ($\pm$0.524) \\
			\textbf{iris}                & \cellcolor[rgb]{ 1,  .922,  .518}1.8581 ($\pm$0.8)         & \cellcolor[rgb]{ .388,  .745,  .482}1.7806 ($\pm$0.727) & \cellcolor[rgb]{ .973,  .412,  .42}2.3613 ($\pm$0.796) \\
			\textbf{mushroom}            & \cellcolor[rgb]{ .388,  .745,  .482}1.5204 ($\pm$0.581)    & \cellcolor[rgb]{ 1,  .922,  .518}1.5484 ($\pm$0.527)    & \cellcolor[rgb]{ .973,  .412,  .42}2.9312 ($\pm$0.289) \\
			\textbf{parkinsons}          & \cellcolor[rgb]{ .388,  .745,  .482}1.557 ($\pm$0.624)     & \cellcolor[rgb]{ 1,  .922,  .518}1.6011 ($\pm$0.591)    & \cellcolor[rgb]{ .973,  .412,  .42}2.8419 ($\pm$0.445) \\
